Cluster Difference Imaging Photometric Survey (CDIPS) II. TOI$\,$837: A Validated Saturn-Sized Planet in IC~2602

### 2020-07-20 paper/ms.tex
Incorporate GB suggestions (part 1)

\begin{abstract}
  We report the discovery of TOI 837.01 and its validation as a
  transiting planet.  We characterize the system using data from the
  NASA TESS mission, the ESA Gaia mission, ground-based photometry from El Sauce
  and ASTEP400, and spectroscopy from CHIRON, FEROS, and Veloce.  We
  find that TOI$\,$837 is a $T=9.9$ G0/F9 dwarf in the southern open
  cluster IC 2602.  The star and planet are therefore $35^{+11}_{-5}$
  million years old. Combining the transit photometry
  with a prior on the stellar parameters derived from the cluster
  color-magnitude diagram, we find that the 
  planet is warm ($P = 8.3\,{\rm d}$) and
  slightly smaller than Jupiter ($R_{\rm p} = 0.80^{+0.09}_{-0.03} \,R_{\rm Jup}$). 
  The transits are either grazing or nearly grazing.  From radial velocity
  monitoring, we limit the minimum mass to less than 1.20 $M_{\rm
  Jup}$ (3$\sigma$).  Grazing transits are a cause for concern, as
  they are usually indicative of astrophysical false positive
  scenarios.  Our follow-up data show that such scenarios are highly
  unlikely.  Our combined multi-color photometry, high-resolution
  imaging, and radial velocities rule out hierarchical eclipsing
  binary scenarios.  Background eclipsing binary scenarios, though
  limited by speckle imaging, formally remain a 0.2\% possibility.
  TOI 837.01 is therefore a validated adolescent exoplanet.  Further
  observations of its stellar obliquity, atmosphere, and mass should
  confirm its planetary nature beyond doubt, and could improve our
  understanding of how the physical and orbital properties of
  exoplanets change in time.
\end{abstract}

@@

The transit method was comparatively slow to catch up.  Early deep
transit searches of open clusters by many groups did not yield
definitive planet detections
\citep{mochejska_planets_2005,mochejska_planets_2006,burke_survey_2006,aigrain_monitor_2007,irwin_monitordata_2007,miller_monitor_2008,pepper_photometric_2008,hartman_MMT_IV_2009}.
These searches were typically sensitive to planets larger than
Jupiter, on $\lesssim 3$ day orbital periods.  Hot Jupiter occurrence
rate limits were derived at the $\lesssim 5\%$ level \citep[{\it
e.g.},][]{burke_survey_2006,hartman_MMT_IV_2009}.  The modern 0.5-1\%
occurrence rate suggests that these early transit surveys needed a
greater data volume, at higher precision for detection to be possible
\citep{mayor_harps_2011,wright_frequency_2012,howard_planet_2012,petigura_metallicity_2018}.

@@

The discoveries made by K2 through its surveys of Taurus, the Hyades,
Praesepe, and Upper Sco were a major inspiration for the present work
\citep[{\it
e.g.},][]{Mann_K2_25_2016,obermeier_k2_2016,Mann_et_al_2017,vanderburg_zeitVII_2018,ciardi_k2-136_2018,livingston_three_2018,mann_ZEITVI_2018,rizzuto_zeitVIII_2018,livingston_k2-264_2019}.
Observations with K2 convincingly showed that at least some close-in
planets must form within about 10 Myr
\citep{Mann_K2_33b_2016,David_et_al_2017}.  They also led to the first
hints that young planets in clusters may in fact be qualitatively different from
their field counterparts.  For instance, based on its observed mass,
radius, and UV environment, the 700$\,$Myr K2-100b is probably
actively losing its atmosphere, and should become a bare rocky planet
over the next few hundred Myr
\citep{Mann_et_al_2017,barragan_radial_2019}.  The four transiting
planets in V1298~Tau (23$\,$Myr) are also likely to be actively
photoevaporating, and could represent a precursor to Kepler's compact
multiple systems \citep{david_four_2019,david_warm_2019}.

@@

Figure~\ref{fig:tessphot} shows the data.  The dominant modulation
induced by starspots coming into and out of view has a peak-to-peak
amplitude of about 2.3\%, and a period of about 3 days.  The dips
suggestive of a grazing transiting planet recur roughly every 8 days,
and have a depth of about 0.4\%.  A few flares are visible.  A
phase-folded view of the TESS transits with starspot variability
removed is shown in Figure~\ref{fig:tessphot}. Our fitting procedure
for the models shown in these plots is described in
Section~\ref{subsec:planet}.

@@

Between 25 July 2014 and 23 May 2016, the ESA Gaia satellite measured
about 300 billion centroid positions of 1{.}6 billion stars.  The
positions, proper motions, and parallaxes of the brighest 1{.}3
billion were calculated for the second data release (DR2)
\citep{gaia_collaboration_gaia_2016,lindegren_gaiasoln_2018,gaia_collaboration_gaia_2018}.
\tn\ was assigned the Gaia DR2 identifier 5251470948229949568, and had
276 ``good'' astrometric observations. Its brightness was measured in
the $G$, $Rp$, and $Bp$ bands of the Radial Velocity Spectrometer
\citep{cropper_gaia_2018,evans_gaia_2018}.

The Gaia imaging, reduced to its point-source catalog, provides the
initial context for analyzing the TESS data.  Stars brighter than
$T=16$, as queried from the Gaia DR2 source catalog, are shown with
white circles in Figure~\ref{fig:scene}, overlaid on the TESS image.
Given its galactic latitude of $b=-6^\circ$, it is not surprising that
the field of \tn\ is crowded.  The resolved stars that were of
immediate concern for our false positive analysis were as follows.
\begin{itemize}
  %
  \item \tn\ $\equiv$ TIC 460205581 ($T=9.9$). The target star.
  %
  \item Star A $\equiv$ TIC 847769574 ($T=14.6$), $2.3''$ west. The
    proper motions and parallax of this star imply it is comoving with
    \tn\ and that the two stars are separated by $6.6\pm 0.1\,{\rm pc}$.
    Star A is therefore likely an \cn\ member, but unlikely to be a bound
    binary compnaion.
  %
  \item Star B $\equiv$ TIC 460205587 ($T=13.1$), $5.4''$ north.  The
    Gaia parallax implies this is a giant background star.
\end{itemize}
An additional source, TIC 847769581, is $4.9''$ from the target, but
too faint ($T=18.8$) to be the source of the observed transit signal.

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=.49\textwidth]{f2b.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Ground-based follow-up photometry.} The data were acquired
    using the 0.36m at El Sauce and the 0.40m ASTEP400 at Dome C.
    Black points are binned to 10-minute intervals.  The gray line is
    the best-fit model to the combined TESS and ground-based data.
    Red and blue lines show $2\sigma$ lower limits on the transit depths in the
    Cousins-R and Johnson-B bandpasses used to rule out specific false
    positive scenarios (see Section~\ref{subsec:colorphot}).
		\label{fig:groundphot}
	}
\end{figure}

@@

\subsubsection{El Sauce 0.36m}

\paragraph{Acquisition and reduction}
We observed four transits with the 0.36m at Observatario El Sauce,
located in the R\'io Hurtado Valley in Chile, and operated by
co-author P{.}~Evans.  The observations were obtained in Cousins-R
band on the nights of 1 April 2020 and 26 April 2020, Cousins-I band
on the night of 21 May 2020, and Johnson-B band on the night of 14
June 2020.  The final 14 June transit began shortly after twilight.

@@

\paragraph{Custom aperture analysis}
Based solely on the TESS data, both Star A and Star B were possible
sources of blended eclipsing binary signals.  The typical FWHM for
stars in the El Sauce observations was $\approx 2.3''$, with a
variance of $\approx 0.2''$.  Star B is resolved in the 0.36m images;
Star A is not.

@@

To assess the possibility that Star A is an eclipsing body, we created
light curves with a custom set of circular apertures with radii of
$2.1''$ and positions ranging from Star A (2.3$''$ west of \tn) to
2.3$''$ east of \tn.  We did not detect any variation of the transit
depth along this line of light curves. The apertures east of \tn\
exclude over 90\% of the flux from Star A.  The eclipse on Star A
would therefore need to have depth greater than unity to produce the
observed eclipse depth.  We therefore interpret the lack of asymmetry
between the western-most (centered on Star A) and eastern-most
(furthest from Star A) light curves as conclusive evidence that \tn\
is the source of the transit signal to within $\approx2.0''$.  To
verify self-consistency, we checked that the maximum dilution from
Star A ($\approx 1\%$) is less than the uncertainty of the transit
depth measurements ($\approx 15\%$), and so the lack of variation of
transit depth with aperture location is consistent with \tn\ being the
source of transits.

@@

We observed three transits with the 0.40m ASTEP telescope at the
Concordia base on the Antarctic Plateau \citep{daban_astep_2010}.
Concordia base is operated jointly by the French and Italian polar
institutes, IPEV and PNRA.  Its position on the Antarctic Plateau
allows it to take advantage of
the continuous night during Austral winter.  The weather is of
photometric quality for about two-thirds of each winter
\citep{crouzet_four_2018}.

@@

\tn\ was observed with ASTEP on 12 May 2020, 29 May 2020, 14 June
2020, and 23 June 2020 (UT) with a cadence of $50\,$s (exposure time
of $25\,$s, readout and processed overhead of $25\,$s).  Except for 12
May, our observations were conducted under stable weather conditions,
with clear skies, temperatures of about $-70^\circ$C, and wind speeds
inferior to 5\,ms$^{-1}$. Due to their poor quality, we exclude from
the analysis all data collected on May 12. We found that the optimal
calibrated light curves of \tn\ correspond to an 11 pixel (10\,arcsec)
and 14 pixel (12\,arcsec) radius aperture for observations carried out
on June and May, respectively.  The data are reported in
Table~\ref{tab:phot}, and plotted in Figure~\ref{fig:groundphot}.

@@

		\vspace{-0.3cm}
		\subfloat{
			\includegraphics[width=0.47\textwidth]{f3.pdf}
		}
	\end{center}
	\vspace{-0.6cm}
	\caption{
    {\bf Speckle-imaging and velocimetry of \tn.} {\it Top:}
    SOAR HRCam contrast limits derived from point-source
    injection-recovery experiments. Star A ($\Delta T=4.7$, $2.3''$
    west) is detected, and is also a
    resolved Gaia source.  It is co-moving with \tn, and its parallax
    and on-sky position imply that it is physically separated from
    \tn\ by $6.6\pm 0.1\,{\rm pc}$.  {\it Middle:} Radial velocity
    (RV) measurements, with best-fit instrument offsets and jitter
    terms included.  The expected scatter from starspots based on
    $v\sin i$ and the photometric modulation amplitude is of order
    300m$\,$s$^{-1}$.  {\it Bottom:} RV measurements phased to the
    orbital ephemeris of \pn.  The planet is not detected.  The black
    line shows a circular Keplerian orbit representing the $3\sigma$
    upper mass limit.
		\label{fig:followup}
	}
\end{figure}

@@

\subsubsection{SMARTS 1.5m / CHIRON}
\label{subsec:chiron}

We acquired nine spectra using CHIRON at the SMARTS 1.5m telescope at
Cerro Tollo Inter-American Observatory, Chile
\citep{tokovinin_chironfiber_2013}.  Six met our signal-to-noise
requirements for radial velocity measurements and stellar parameter
extraction.  We used CHIRON in its image slicer configuration,
yielding a spectral resolution of $\approx 79{,}000$ across
415--880$\,$nm.

@@

To derive the stellar parameters, we matched the set of CHIRON spectra
against a library of observed spectra, previously
obtained using the Tillinghast Reflect Echelle Spectrograph
\citep[TRES,][]{furesz_tres_2008} on the 1.5\,m reflector at the Fred
Lawrence Whipple Observatory (FLWO), Arizona, US, and classified using
the Stellar Parameter Classification pipeline
\citep{buchhave_hatp16b_class_2010}.  We found the best matching
stellar parameters to be $T_\mathrm{eff} = 5899 \pm 55$K, $\log g =
4.496 \pm 0.011$ dex, and $\mathrm{[Fe/H]} -0.069 \pm 0.042$ dex.

@@

\subsubsection{FEROS}
TOI 837.01 was monitored with the FEROS echelle spectrograph
\citep{kaufer_commissioning_1999}, mounted on the MPG 2.2m telescope
at the ESO La Sille Observatory, in Chile. FEROS has a resolution of
$\approx$48,000 across a spectral range of 350–920 nm. It has a
remarkably high efficiency of $\approx$20\%. We obtained 13 spectra of
\tn\ between July 5 of 2019 and March 14 of 2020 in the context of the
Warm gIaNts with tEss (WINE) collaboration, which focuses on the
systematic characterization of TESS transiting giant planets with
moderately long orbital periods \citep[{\it
e.g.},][]{brahm:2019,jordan:2020}.  We adopted exposure times of 500
and 600 seconds and the observations were performed with the
simultaneous calibration mode for tracing the instrumental velocity
variations with a comparison fiber illuminated with a ThAr lamp. FEROS
data was processed with the \texttt{ceres} pipeline
\citep{brahm_2017_ceres}, which delivers precision radial velocities
and bisector span measurements through cross-correlation of the
extracted spectra with a binary mask resembling the properties of a
G2V star. The radial velocities are given in Table~\ref{tab:rvs},
and shown in Figure~\ref{fig:followup}.

\subsubsection{Veloce}
We acquired 34 spectra over 10 visits of \tn\ using the Veloce
spectrograph, mounted on the AAT 4.0m telescope at Siding Spring
Observatory near Coonabarabran, Australia \citep{gilbert_veloce_2018}.
In the ``Rosso'' instrument-mode, Veloce provides coverage from
600--950$\,$nm at a spectral resolution of $\approx 80{,}000$.  Many
of the exposures were taken in average or poor seeing conditions, when
fiber-to-fiber cross-contamination on the IFU-style fiber feed is
strongest.  To reduce the spectra to velocities, we cross-correlated
against a high S/N template of $\delta$ Pavonis.  The velocity RMS
seen across each visit was hundreds of meters per second, likely due
to uncorrected fiber-to-fiber cross-contamination.  For analysis
purposes, we averaged across each visit, and set the velocity
uncertainties to be the standard deviation of the per-visit exposures.
The velocities are given in Table~\ref{tab:rvs}, and shown in
Figure~\ref{fig:followup}.

@@

If the transit were box-shaped, this argument could be extended to
even more restrictive depths \citep[{\it
e.g.},][]{seager_unique_2003,vanderburg_hr858_2019,rizzuto_tess_2020}
Since the transits of \tn\ are grazing, the second and third
contact points do not occur, and the shape of the transit is not
restrictive.

@@

To convert from theoretical effective temperatures and bolometric
luminosities to expected magnitudes in instrumental bandpasses, we
made the simplying assumption that all sources had blackbody spectra.
Using the theoretical stellar parameters and the measured transmission
functions \citep{tokovinin_ten_2018}, we then calculated the apparent
magnitudes of stellar companions of different masses, and interpolated
to produce the scale shown on the upper-right in
Figure~\ref{fig:fpscenario}.

@@

We fitted for the observed depths in different bandpasses using a
similar machinery as described in Section~\ref{subsec:planet}.  We
fitted each ground-based transit individually for the planet-to-star
size ratio, the impact parameter, and a local quadratic trend (the
ephemeris was assumed from an initial fit of only the TESS data).  The
corresponding $2$-$\sigma$ limits on the transit depths in Cousins-R
and Johnson-B band light curves were 2.82 and 1.77$\,$ppt,
respectively, and are shown in Figure~\ref{fig:groundphot}.
Particularly in our Johnson-B light curve, the transit depth is
correlated with the mean and linear slope of the light curve: a
smaller depth is allowed if the data are fitted with a larger linear
slope and a larger mean.  Our quoted limits marginalize over these
correlations, and the depth measurement itself is nearly Gaussian.

@@

Archival SERC-J and AAO-SES plates are available for the \tn\
field\footnote{\url{https://archive.stsci.edu/cgi-bin/dss_form}}.
These plates were acquired in 1982 and 1992, respectively.  For high
proper motion stars archival imagery can be used to detect slowly
moving background stars that might be an astrophysical false-positive
source ({\it e.g.}, \citealt{huang_pimen_2018},
\citealt{vanderburg_hr858_2019}).  However \tn\ has only moved
$\approx0.7''$ between 1982 and present, in comparison to the
$\approx2.0''$ FWHM of the target on the plates.  We therefore cannot
resolve it with great confidence from background sources not already
resolved through more modern imaging.

@@

The \cn\ cluster is about 150$\,$pc from the Earth, and is near the
galactic plane with $(l,b)\approx(289.6^\circ, -5.0^\circ)$
\citep{cantatgaudin_gaia_2018}.  It is also sometimes called the
$\theta$ Carinae cluster, after its brightest member.  While \cn\ is
close to the Lower Centaurus Crux subgroup of the Scorpio-Centaurus
OB2 association in both position and proper motion space, its older
age and clear kinematic separation indicate that it is a distinct
stellar population
\citep{de_zeeuw_hipparcos_1999,damiani_stellar_2019}.

@@

We measured the rotation period from the PDCSAP light curve using the
Lomb-Scargle periodogram implemented in \texttt{astropy}
\citep{lomb_1976,scargle_studies_1982,vanderplas_periodograms_2015}.
We fitted the light curve without masking out the transits or flares,
as these represent a small fraction of the overall time series.  To
derive the uncertainty on the best period, we fitted a gaussian to the
dominant peak, after first ensuring that we had oversampled the
initial frequency grid.  This gave a rotation period of $P_{\rm rot} =
2.987 \pm 0.056\,{\rm d}$ when allowing for a single Fourier terms in
the periodogram model, and $P_{\rm rot} = 3.004 \pm 0.053\,{\rm d}$
when allowing for two Fourier terms.  As the second model provides a
better fit to the data, we adopt the second measurement.

>>>>

\begin{abstract}
  We report the discovery of TOI 837.01 and its validation as a
  transiting planet.  We characterize the system using data from the
  NASA TESS mission, the ESA Gaia mission, ground-based photometry from El Sauce
  and ASTEP400, and spectroscopy from the CHIRON, FEROS, and Veloce
  spectrographs.  We
  find that TOI$\,$837 is a $T=9.9\,{\rm mag}$ G0/F9 dwarf in the southern open
  cluster IC 2602.  The star and planet are therefore $35^{+11}_{-5}$
  million years old. Combining the transit photometry
  with a prior on the stellar parameters derived from the cluster
  color-magnitude diagram, we find that the 
  planet is warm ($P = 8.3\,{\rm d}$) and
  slightly smaller than Jupiter ($R_{\rm p} = 0.80^{+0.09}_{-0.03} \,R_{\rm Jup}$). 
  The transits are either grazing or nearly grazing.  From radial velocity
  monitoring, we limit the minimum mass to less than 1.20 $M_{\rm
  Jup}$ (3$\sigma$).  Grazing transits are a cause for concern, as
  they are usually indicative of astrophysical false positive
  scenarios.  Our follow-up data show that such scenarios are highly
  unlikely.  Our combined multi-color photometry, high-resolution
  imaging, and radial velocities rule out hierarchical eclipsing
  binary scenarios.  Background eclipsing binary scenarios, though
  limited by speckle imaging, formally remain a 0.2\% possibility.
  TOI 837.01 is therefore a validated adolescent exoplanet.  Further
  observations of its stellar obliquity, atmosphere, and mass should
  confirm its planetary nature beyond doubt, and could improve our
  understanding of how the physical and orbital properties of
  exoplanets change in time.
\end{abstract}

@@

The transit method was comparatively slow to catch up.  Early deep
transit searches of open clusters by many groups did not yield
definitive planet detections
\citep{mochejska_planets_2005,mochejska_planets_2006,burke_survey_2006,aigrain_monitor_2007,irwin_monitordata_2007,miller_monitor_2008,pepper_photometric_2008,hartman_MMT_IV_2009}.
These searches were typically sensitive to planets larger than
Jupiter, on $\lesssim 3$ day orbital periods.  Hot Jupiter occurrence
rate limits were derived at the $\lesssim 5\%$ level \citep[{\it
e.g.},][]{burke_survey_2006,hartman_MMT_IV_2009}.  The modern 0.5-1\%
occurrence rate suggests that these early transit surveys would have needed a
greater data volume at higher precision for detection to be possible
\citep{mayor_harps_2011,wright_frequency_2012,howard_planet_2012,petigura_metallicity_2018}.

@@

The discoveries made by K2 through its surveys of Taurus, the Hyades,
Praesepe, and Upper Sco were a major inspiration for the present work
\citep[{\it
e.g.},][]{Mann_K2_25_2016,obermeier_k2_2016,Mann_et_al_2017,vanderburg_zeitVII_2018,ciardi_k2-136_2018,livingston_three_2018,mann_ZEITVI_2018,rizzuto_zeitVIII_2018,livingston_k2-264_2019}.
Observations with K2 convincingly showed that at least some close-in
planets must form within about 10 Myr
\citep{Mann_K2_33b_2016,David_et_al_2017}.  They also led to the first
hints that young planets in clusters may in fact be qualitatively different from
their field counterparts.  For instance, based on its observed mass,
radius, and UV environment, the 700$\,$Myr K2-100b is probably
actively losing its atmosphere, and should become a bare rocky planet
over the next few hundred Myr
\citep{Mann_et_al_2017,barragan_radial_2019}.  The four transiting
planets around V1298~Tau (23$\,$Myr) are also likely to be actively
photoevaporating, and could represent a precursor to Kepler's compact
multiple systems \citep{david_four_2019,david_warm_2019}.

@@

Figure~\ref{fig:tessphot} shows the data.  The dominant modulation
induced by starspots coming into and out of view has a peak-to-peak
amplitude of about 2.3\%, and a period of about 3 days.  The dips
suggestive of a grazing transiting planet recur roughly every 8 days,
and have a depth of about 0.4\%.  A few flares are also visible.  A
phase-folded view of the TESS transits with starspot variability
removed is shown in Figure~\ref{fig:tessphot}. Our fitting procedure
for the models shown in these plots is described in
Section~\ref{subsec:planet}.

@@

Between 25 July 2014 and 23 May 2016, the ESA Gaia satellite measured
about 300 billion centroid positions of 1{.}6 billion stars.  The
positions, proper motions, and parallaxes of the brightest 1{.}3
billion were calculated for the second data release (DR2)
\citep{gaia_collaboration_gaia_2016,lindegren_gaiasoln_2018,gaia_collaboration_gaia_2018}.
\tn\ was assigned the Gaia DR2 identifier 5251470948229949568, and had
276 ``good'' astrometric observations. Its brightness was measured in
the $G$, $Rp$, and $Bp$ bands of the Radial Velocity Spectrometer
\citep{cropper_gaia_2018,evans_gaia_2018}.

The Gaia imaging, reduced to its point-source catalog, provides the
initial context for analyzing the TESS data.  Stars brighter than
$T=16$, as queried from the Gaia DR2 source catalog, are shown with
white circles in Figure~\ref{fig:scene}, overlaid on the TESS image.
Given its galactic latitude of $b=-6^\circ$, it is not surprising that
the field of \tn\ is crowded.  The resolved stars that were of
immediate concern for our false positive analysis were as follows.
\begin{itemize}
  %
  \item \tn\ $\equiv$ TIC 460205581 ($T=9.9$). The target star.
  %
  \item Star A $\equiv$ TIC 847769574 ($T=14.6$), $2.3''$ West. The
    proper motions and parallax of this star imply it is comoving with
    \tn\ and that the two stars are separated by $6.6\pm 0.1\,{\rm pc}$.
    Star A is therefore likely an \cn\ member, but unlikely to be a bound
    binary compnaion.
  %
  \item Star B $\equiv$ TIC 460205587 ($T=13.1$), $5.4''$ North.  The
    Gaia parallax implies this is a giant background star.
\end{itemize}
An additional source, TIC 847769581, is $4.9''$ from the target, but
too faint ($T=18.8$) to be the source of the observed transit signal.

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=.49\textwidth]{f2b.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Ground-based follow-up photometry.} The data were acquired
    using the 0.36$\,$m at El Sauce and the 0.40$\,$m ASTEP400 at Dome C.
    Black points are binned to 10-minute intervals.  The gray line is
    the best-fit model to the combined TESS and ground-based data.
    Red and blue lines show $2\sigma$ lower limits on the transit depths in the
    Cousins-R and Johnson-B bandpasses used to rule out specific false
    positive scenarios (see Section~\ref{subsec:colorphot}).
		\label{fig:groundphot}
	}
\end{figure}

@@

\subsubsection{El Sauce 0.36$\,$m}

\paragraph{Acquisition and reduction}
We observed four transits with the 0.36$\,$m at Observatario El Sauce,
located in the R\'io Hurtado Valley in Chile, and operated by
co-author P{.}~Evans.  The observations were obtained in Cousins-R
band on the nights of 1 April 2020 and 26 April 2020, Cousins-I band
on the night of 21 May 2020, and Johnson-B band on the night of 14
June 2020.  The final 14 June transit began shortly after twilight.

@@

\paragraph{Custom aperture analysis}
Based solely on the TESS data, both Star A and Star B were possible
sources of blended eclipsing binary signals.  The typical FWHM for
stars in the El Sauce observations was $\approx 2.3''$, with a
variance of $\approx 0.2''$.  Star B is resolved in the 0.36$\,$m images;
Star A is not.

@@

To assess the possibility that Star A is an eclipsing body, we created
light curves with a custom set of circular apertures with radii of
$2.1''$ and positions ranging from Star A (2.3$''$ West of \tn) to
2.3$''$ East of \tn.  We did not detect any variation of the transit
depth along this line of light curves. The apertures East of \tn\
exclude over 90\% of the flux from Star A.  The eclipse on Star A
would therefore need to have depth greater than unity to produce the
observed eclipse depth.  We therefore interpret the lack of asymmetry
between the Western-most (centered on Star A) and Eastern-most
(furthest from Star A) light curves as conclusive evidence that \tn\
is the source of the transit signal to within $\approx2.0''$.  To
verify self-consistency, we checked that the maximum dilution from
Star A ($\approx 1\%$) is less than the uncertainty of the transit
depth measurements ($\approx 15\%$), and so the lack of variation of
transit depth with aperture location is consistent with \tn\ being the
source of transits.

@@

We observed three transits with the 0.40$\,$m ASTEP telescope at the
Concordia base on the Antarctic Plateau \citep{daban_astep_2010}.
Concordia base is operated jointly by the French and Italian polar
institutes, IPEV and PNRA.  Its position on the Antarctic Plateau
allows it to take advantage of
the continuous night during Austral winter.  The weather is of
photometric quality for about two-thirds of each winter
\citep{crouzet_four_2018}.

@@

\tn\ was observed with ASTEP on 12 May 2020, 29 May 2020, 14 June
2020, and 23 June 2020 (UT) with a cadence of $50\,$s (exposure time
of $25\,$s, readout and processed overhead of $25\,$s).  Except for 12
May, our observations were conducted under stable weather conditions,
with clear skies, temperatures of about $-70^\circ$C, and wind speeds
less than 5\,ms$^{-1}$. Due to their poor quality, we exclude from
the analysis all data collected on May 12. We found that the optimal
calibrated light curves of \tn\ correspond to an 11 pixel (10\,arcsec)
and 14 pixel (12\,arcsec) radius aperture for observations carried out
on June and May, respectively.  The data are reported in
Table~\ref{tab:phot}, and plotted in Figure~\ref{fig:groundphot}.

@@

		\vspace{-0.3cm}
		\subfloat{
			\includegraphics[width=0.47\textwidth]{f3.pdf}
		}
	\end{center}
	\vspace{-0.6cm}
	\caption{
    {\bf Speckle-imaging and velocimetry of \tn.} {\it Top:}
    SOAR HRCam contrast limits derived from point-source
    injection-recovery experiments. Star A ($\Delta T=4.7$, $2.3''$
    West) is detected, and is also a
    resolved Gaia source.  It is co-moving with \tn, and its parallax
    and on-sky position imply that it is physically separated from
    \tn\ by $6.6\pm 0.1\,{\rm pc}$.  {\it Middle:} Radial velocity
    (RV) measurements, with best-fit instrument offsets and jitter
    terms included.  The expected scatter from starspots based on
    $v\sin i$ and the photometric modulation amplitude is of order
    300m$\,$s$^{-1}$.  {\it Bottom:} RV measurements phased to the
    orbital ephemeris of \pn.  The planet is not detected.  The black
    line shows a circular Keplerian orbit representing the $3\sigma$
    upper mass limit.
		\label{fig:followup}
	}
\end{figure}

@@

\subsubsection{SMARTS 1.5$\,$m / CHIRON}
\label{subsec:chiron}

We acquired nine spectra using CHIRON at the SMARTS 1.5$\,$m telescope at
Cerro Tollo Inter-American Observatory, Chile
\citep{tokovinin_chironfiber_2013}.  Six met our signal-to-noise
requirements for radial velocity measurements and stellar parameter
extraction.  We used CHIRON in its image slicer configuration,
yielding a spectral resolution of $\approx 79{,}000$ across
415--880$\,$nm.

@@

To derive the stellar parameters, we matched the set of CHIRON spectra
against a library of observed spectra, previously
obtained using the Tillinghast Reflect Echelle Spectrograph
\citep[TRES,][]{furesz_tres_2008} on the 1.5\,m reflector at the Fred
Lawrence Whipple Observatory (FLWO), Arizona, USA, and classified using
the Stellar Parameter Classification pipeline
\citep{buchhave_hatp16b_class_2010}.  We found the best matching
stellar parameters to be $T_\mathrm{eff} = 5899 \pm 55$K, $\log g =
4.496 \pm 0.011$ dex, and $\mathrm{[Fe/H]} = -0.069 \pm 0.042$ dex.

@@

\subsubsection{FEROS}
TOI 837.01 was monitored with the FEROS echelle spectrograph
\citep{kaufer_commissioning_1999}, mounted on the MPG 2.2$\,$m telescope
at the ESO La Sille Observatory, in Chile. FEROS has a resolution of
$\approx$48,000 across a spectral range of 350–920 nm. It has a
remarkably high efficiency of $\approx$20\%. We obtained 13 spectra of
\tn\ between July 5 of 2019 and March 14 of 2020 in the context of the
Warm gIaNts with tEss (WINE) collaboration, which focuses on the
systematic characterization of TESS transiting giant planets with
moderately long orbital periods \citep[{\it
e.g.},][]{brahm:2019,jordan:2020}.  We adopted exposure times of 500
and 600 seconds and the observations were performed with the
simultaneous calibration mode for tracing the instrumental velocity
variations with a comparison fiber illuminated with a ThAr lamp. FEROS
data was processed with the \texttt{ceres} pipeline
\citep{brahm_2017_ceres}, which delivers precision radial velocities
and bisector span measurements through cross-correlation of the
extracted spectra with a binary mask resembling the properties of a
G2V star. The radial velocities are given in Table~\ref{tab:rvs},
and shown in Figure~\ref{fig:followup}.

\subsubsection{Veloce}
We acquired 34 spectra over 10 visits of \tn\ using the Veloce
spectrograph, mounted on the AAT 3.9$\,$m telescope at Siding Spring
Observatory near Coonabarabran, Australia \citep{gilbert_veloce_2018}.
In the ``Rosso'' instrument-mode, Veloce provides coverage from
600--950$\,$nm at a spectral resolution of $\approx 80{,}000$.  Many
of the exposures were taken in average or poor seeing conditions, when
fiber-to-fiber cross-contamination on the IFU-style fiber feed is
strongest.  To reduce the spectra to velocities, we cross-correlated
against a high S/N template of $\delta$ Pavonis, because with spectral
type G8 IV it was the closest \tn\ analog available in the Veloce
spectral database.  The velocity RMS seen across each visit was
hundreds of meters per second, likely due to uncorrected
fiber-to-fiber cross-contamination.  For analysis purposes, we
averaged across each visit, and set the velocity uncertainties to be
the standard deviation of the per-visit exposures.  The velocities are
given in Table~\ref{tab:rvs}, and shown in Figure~\ref{fig:followup}.

@@

If the transit were box-shaped, this argument could be extended to
even more restrictive depths \citep[{\it
e.g.},][]{seager_unique_2003,vanderburg_hr858_2019,rizzuto_tess_2020}.
Since the transits of \tn\ are grazing, the second and third
contact points do not occur, and the shape of the transit is not
restrictive.

@@

To convert from theoretical effective temperatures and bolometric
luminosities to expected magnitudes in instrumental bandpasses, we
made the simplifying assumption that all sources had blackbody spectra.
Using the theoretical stellar parameters and the measured transmission
functions \citep{tokovinin_ten_2018}, we then calculated the apparent
magnitudes of stellar companions of different masses, and interpolated
to produce the scale shown on the upper-right in
Figure~\ref{fig:fpscenario}.

@@

We fitted for the observed depths in different bandpasses using a
similar machinery as described in Section~\ref{subsec:planet}.  We
fitted each ground-based transit individually for the planet-to-star
size ratio, the impact parameter, and a local quadratic trend (the
ephemeris was assumed from an initial fit of only the TESS data).  The
corresponding $2$-$\sigma$ lower limits on the transit depths in Cousins-R
and Johnson-B band light curves were 2.82 and 1.77$\,$ppt,
respectively, and are shown in Figure~\ref{fig:groundphot}.
Particularly in our Johnson-B light curve, the transit depth is
correlated with the mean and linear slope of the light curve: a
smaller depth is allowed if the data are fitted with a larger linear
slope and a larger mean.  Our quoted limits marginalize over these
correlations, and the depth measurement itself is nearly Gaussian.

@@

Archival SERC-J and AAO-SES plates are available for the \tn\
field\footnote{\url{https://archive.stsci.edu/cgi-bin/dss_form}}.
These plates were acquired in 1982 and 1992, respectively.  For high
proper motion stars archival imagery can be used to detect slowly
moving background stars that might be an astrophysical false-positive
source \citep[{\it e.g.},][]{bakos_stellar_2006,huang_pimen_2018,vanderburg_hr858_2019}.  However \tn\ has only moved
$\approx0.7''$ between 1982 and present, in comparison to the
$\approx2.0''$ FWHM of the target on the plates.  We therefore cannot
resolve it with great confidence from background sources not already
resolved through more modern imaging.

@@

The \cn\ cluster is about 150$\,$pc from the Earth, and is near the
galactic plane with $(l,b)\approx(289.6^\circ, -5.0^\circ)$
\citep{cantatgaudin_gaia_2018}.  It is also sometimes called the
$\theta$ Carinae cluster, after its brightest member, or also the
``Southern Pleiades''.  While \cn\ is close to the Lower Centaurus
Crux subgroup of the Scorpio-Centaurus OB2 association in both
position and proper motion space, its older age and clear kinematic
separation indicate that it is a distinct stellar population
\citep{de_zeeuw_hipparcos_1999,damiani_stellar_2019}.

@@

We measured the rotation period from the TESS PDCSAP light curve using the
Lomb-Scargle periodogram implemented in \texttt{astropy}
\citep{lomb_1976,scargle_studies_1982,vanderplas_periodograms_2015}.
We fitted the light curve without masking out the transits or flares,
as these represent a small fraction of the overall time series.  To
derive the uncertainty on the best period, we fitted a Gaussian to the
dominant peak, after first ensuring that we had oversampled the
initial frequency grid.  This gave a rotation period of $P_{\rm rot} =
2.987 \pm 0.056\,{\rm d}$ when allowing for a single Fourier terms in
the periodogram model, and $P_{\rm rot} = 3.004 \pm 0.053\,{\rm d}$
when allowing for two Fourier terms.  As the second model provides a
better fit to the data, we adopt the second measurement.
